---
title: "This is a Markdown just for fun"
author: me
output: bookdown::html_document2
bibliography: new_bib.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = "center") # chunk option for all of the document)
```

```{r, echo=FALSE}
library(test2017package)
library(tidyverse)
library(bookdown)
library(knitr)
library(ggplot2)
```


I need to cite this guy [@zimmermann2009estimations].

Also I need to cite this Fahrig - guy [-@fahrig1973nachweis]

# Trials

## What am I doing here?
I am just trying around and creating stuff.

```{r try, echo=TRUE, cache=TRUE}
anlaeg <- read.csv("../data/anlaeg_all_25832.csv") 
  anlaeg2<-anlaeg[1:10,]
```

This data (above) is going to the cache. But now we continue calculating and create something like a table consisting senselessly transformed data.

```{r, maketable, echo=TRUE, cache=FALSE}
dependson='try'
new_function(anlaeg2$fra_aar) -> kya
another_function(kya) -> percent
table <- cbind.data.frame(kya,percent)
```


If I now have done this great stuff, I can see, whether we can see this in our Table \@ref(tab:try2) and in the beautiful plot as created in figure \@ref(fig:thisplot).

Yeah?


```{r, try2, echo=FALSE}
dependson='maketable'
knitr::kable(table, 
             caption = "try this")
```



Let's add a plot
```{r, thisplot, fig.cap="This is a wonderful plot, isn't it" }
dependson='try2'
ggplot(table, aes(x=kya,y=percent))+
  geom_point()

```


```{r}
library(binford)
data(LRB)
knitr::kable(head(LRB))
```

